Through the eyes of the teacher

### 2021-02-04 paper_1/paper_1_supplement.Rmd
table GRI

@@

# calculate GRI 
view(et.raw.data)

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations, na.rm = TRUE), 2),
            "GRI" = round(mean(Total_duration_of_whole_fixations) / Number_of_whole_fixations)
            )

@@

>>>>

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

@@

# calculate GRI

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
view(et.raw.table)

@@

```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}

et.plot <- et.raw.data %>%
  ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~Variable)+
    ggtitle("Boxplot with individual points for Number of fixations") +
    xlab("")
et.plot
